Hochschild cohomology of torus equivariant D-modules

### 2018-08-02 paper.tex
Correcting the bibliography

\bibitem{ArinkinGaitsgory:2015:SingularSupport}
Dima Arinkin and Dennis Gaitsgory.
\newblock Singular support of coherent sheaves and the geometric {L}anglands
  conjecture.
\newblock \emph{Selecta Mathematica. New Series}, 21\penalty0 (1):\penalty0
  1--199, 2015.
\newblock ISSN 1022-1824.
\newblock \doi{10.1007/s00029-014-0167-5}.

@@

\bibitem{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup}
David {Ben-Zvi} and David {Nadler}.
\newblock {The Character Theory of a Complex Group}.
\newblock \emph{ArXiv e-prints}, April 2009.

\bibitem{BenZviNadler:arXiv:NonlinearTraces}
David {Ben-Zvi} and David {Nadler}.
\newblock {Nonlinear Traces}.
\newblock \emph{ArXiv e-prints}, May 2013.

\bibitem{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}
Dave Benson, Srikanth~B. Iyengar, and Henning Krause.
\newblock Local cohomology and support for triangulated categories.
\newblock \emph{Annales Scientifiques de l'École Normale Supérieure},
  41\penalty0 (4):\penalty0 573--619, 2008.
\newblock ISSN 0012-9593.

\bibitem{Braverman:LecturesOnAlgebraicDmodules}
Alexander Braverman and Tatyana Chmutova.
\newblock Lectures on algebraic $d$-modules.
\newblock URL
  \url{http://www.math.harvard.edu/~gaitsgde/grad_2009/Dmod_brav.pdf}.

\bibitem{BravermanGaitsgory:2002:GeometricEisensteinSeries}
Alexander Braverman and Dennis Gaitsgory.
\newblock Geometric {E}isenstein series.
\newblock \emph{Inventiones Mathematicae}, 150\penalty0 (2):\penalty0 287--384,
  2002.
\newblock ISSN 0020-9910.
\newblock \doi{10.1007/s00222-002-0237-8}.

\bibitem{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}
V.~Drinfeld and D.~Gaitsgory.
\newblock Compact generation of the category of {D}-modules on the stack of
  {$G$}-bundles on a curve.
\newblock \emph{Cambridge Journal of Mathematics}, 3\penalty0 (1-2):\penalty0
  19--125, 2015.
\newblock ISSN 2168-0930.
\newblock \doi{10.4310/CJM.2015.v3.n1.a2}.

\bibitem{DrinfeldGaitsgory:2013:FinitenessQuestions}
Vladimir Drinfeld and Dennis Gaitsgory.
\newblock On some finiteness questions for algebraic stacks.
\newblock \emph{Geometric and Functional Analysis}, 23\penalty0 (1):\penalty0
  149--294, 2013.
\newblock ISSN 1016-443X.
\newblock \doi{10.1007/s00039-012-0204-5}.

\bibitem{DrinfeldGaitsgory:2014:OnATheoremOfBraden}
Vladimir Drinfeld and Dennis Gaitsgory.
\newblock On a theorem of {B}raden.
\newblock \emph{Transformation Groups}, 19\penalty0 (2):\penalty0 313--358,
  2014.
\newblock ISSN 1083-4362.
\newblock \doi{10.1007/s00031-014-9267-8}.

\bibitem{FrancisGaitsgory:2012:ChiralKoszulDuality}
John Francis and Dennis Gaitsgory.
\newblock Chiral {K}oszul duality.
\newblock \emph{Selecta Mathematica. New Series}, 18\penalty0 (1):\penalty0
  27--87, 2012.
\newblock ISSN 1022-1824.
\newblock \doi{10.1007/s00029-011-0065-z}.

\bibitem{GaitsgoryRozenblyum:2014:CrystalsAndDModules}
Dennis Gaitsgory and Nick Rozenblyum.
\newblock Crystals and {D}-modules.
\newblock \emph{Pure and Applied Mathematics Quarterly}, 10\penalty0
  (1):\penalty0 57--154, 2014.
\newblock ISSN 1558-8599.
\newblock \doi{10.4310/PAMQ.2014.v10.n1.a2}.

@@

\bibitem{Sumihiro:1974:EquivariantCompletions}
Hideyasu Sumihiro.
\newblock Equivariant completion.
\newblock \emph{Journal of Mathematics of Kyoto University}, 14:\penalty0
  1--28, 1974.
\newblock ISSN 0023-608X.
\newblock \doi{10.1215/kjm/1250523277}.

>>>>

\bibitem{ArinkinGaitsgory:2015:SingularSupport}
Dima Arinkin and Dennis Gaitsgory.
\newblock Singular support of coherent sheaves and the geometric {L}anglands
  conjecture.
  \newblock \emph{Selecta Math. (N.S.)}, 21\penalty0 (1):\penalty0
  1--199, 2015.
\newblock ISSN 1022-1824.
\newblock \doi{10.1007/s00029-014-0167-5}.

@@

\bibitem{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup}
David {Ben-Zvi} and David {Nadler}.
\newblock {The Character Theory of a Complex Group}.
\newblock \emph{ArXiv e-prints}, April 2009.
\newblock \href{https://www.arxiv.org/abs/0904.1247}{arXiv:0904.1247}.

\bibitem{BenZviNadler:arXiv:NonlinearTraces}
David {Ben-Zvi} and David {Nadler}.
\newblock {Nonlinear Traces}.
\newblock \emph{ArXiv e-prints}, May 2013.
\newblock \href{https://www.arxiv.org/abs/1305.7175}{arXiv:1305.7175}.

\bibitem{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}
Dave Benson, Srikanth~B. Iyengar, and Henning Krause.
\newblock Local cohomology and support for triangulated categories.
\newblock \emph{Ann. Sci. \'Ec. Norm. Sup\'er. (4)},
  41\penalty0 (4):\penalty0 573--619, 2008.
\newblock ISSN 0012-9593.

\bibitem{Braverman:LecturesOnAlgebraicDmodules}
Alexander Braverman and Tatyana Chmutova.
\newblock Lectures on algebraic $D$-modules.
\newblock URL
  \url{http://www.math.harvard.edu/~gaitsgde/grad_2009/Dmod_brav.pdf}.

\bibitem{BravermanGaitsgory:2002:GeometricEisensteinSeries}
Alexander Braverman and Dennis Gaitsgory.
\newblock Geometric {E}isenstein series.
\newblock \emph{Invent. Math.}, 150\penalty0 (2):\penalty0 287--384,
  2002.
\newblock ISSN 0020-9910.
\newblock \doi{10.1007/s00222-002-0237-8}.

\bibitem{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}
V.~Drinfeld and D.~Gaitsgory.
\newblock Compact generation of the category of {D}-modules on the stack of
  {$G$}-bundles on a curve.
\newblock \emph{Camb. J. Math.}, 3\penalty0 (1-2):\penalty0
  19--125, 2015.
\newblock ISSN 2168-0930.
\newblock \doi{10.4310/CJM.2015.v3.n1.a2}.

\bibitem{DrinfeldGaitsgory:2013:FinitenessQuestions}
Vladimir Drinfeld and Dennis Gaitsgory.
\newblock On some finiteness questions for algebraic stacks.
\newblock \emph{Geom. Funct. Anal.}, 23\penalty0 (1):\penalty0
  149--294, 2013.
\newblock ISSN 1016-443X.
\newblock \doi{10.1007/s00039-012-0204-5}.

\bibitem{DrinfeldGaitsgory:2014:OnATheoremOfBraden}
Vladimir Drinfeld and Dennis Gaitsgory.
\newblock On a theorem of {B}raden.
\newblock \emph{Transform. Groups}, 19\penalty0 (2):\penalty0 313--358,
  2014.
\newblock ISSN 1083-4362.
\newblock \doi{10.1007/s00031-014-9267-8}.

\bibitem{FrancisGaitsgory:2012:ChiralKoszulDuality}
John Francis and Dennis Gaitsgory.
\newblock Chiral {K}oszul duality.
\newblock \emph{Selecta Math. (N.S.)}, 18\penalty0 (1):\penalty0
  27--87, 2012.
\newblock ISSN 1022-1824.
\newblock \doi{10.1007/s00029-011-0065-z}.

\bibitem{GaitsgoryRozenblyum:2014:CrystalsAndDModules}
Dennis Gaitsgory and Nick Rozenblyum.
\newblock Crystals and {D}-modules.
\newblock \emph{Pure Appl. Math. Q.}, 10\penalty0
  (1):\penalty0 57--154, 2014.
\newblock ISSN 1558-8599.
\newblock \doi{10.4310/PAMQ.2014.v10.n1.a2}.

@@

\bibitem{Sumihiro:1974:EquivariantCompletions}
Hideyasu Sumihiro.
\newblock Equivariant completion.
\newblock \emph{J. Math. Kyoto Univ.}, 14:\penalty0
  1--28, 1974.
\newblock ISSN 0023-608X.
\newblock \doi{10.1215/kjm/1250523277}.
